---
title: "visualization_pt1"
author: "Waveley Qiu (wq2162)"
date: "2022=06=23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
library(hexbin)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%",
  cache = TRUE 
)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## Basic Scatterplot

First, a basic plot.

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point() +
  theme_minimal()
```

Now, we can try using pipes.

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point() +
  theme_minimal()
```

Sometimes, we want to save the ggplot we've created into its own object and modify it as needed.

```{r}
plot_weather <- 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax))

plot_weather + 
  geom_point() +
  theme_minimal()
```

## Advanced Scatterplots

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(colour = name)) +
  theme_minimal()
```

Let's make this a little fancier.

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(colour = name), alpha = 0.5) +
  theme_minimal() +
  geom_smooth(se = FALSE)
```

We'll keep making things more complicated (but cool!).

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.5) +
  theme_minimal() +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

Now, let's look at seasonality (and precipitation).

```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = 0.5) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


## Odds and Ends
'
```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_smooth(se = FALSE) +
  theme_minimal()
```

Now a hexagon plot:

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex() +
  theme_minimal()
```

## Univariate Plots

We will just be looking at the distribution of one variable.

First up is the histogram.

```{r}
weather_df %>%
  ggplot(aes(x = tmax)) + 
  geom_histogram() +
  theme_minimal()
```

We can make a slightly better version of the histogram above.

```{r}
# with dodge
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) +
  geom_histogram(position = "dodge", binwidth = 2) +
  theme_minimal()

# without dodge
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) +
  geom_histogram(binwidth = 2) +
  theme_minimal()
```

Density plots are sometimes easier to understand than histograms.

```{r}
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) +
  #geom_density(alpha = 0.4, adjust = 0.5, aes(color = name)) +
  #geom_density(alpha = 0.4, adjust = 0.5, aes(color = "blue")) + <- this didn't work as expected
  geom_density(alpha = 0.4, adjust = 0.5, aes(color = name)) +
  geom_rug(aes(color = name)) +
  theme_minimal()
```

We can also make boxplots.

```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot() +
  theme_minimal()
```

Violin plots are sometimes nice (but people sometimes complain that they don't look like violins).

```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmax)) +
  geom_violin(aes(fill = name), alpha = 0.5) +
  stat_summary(fun = "median", color = "blue") +
  theme_minimal()
```

```{r}
weather_df %>%
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges(scale = 0.85) +
  theme_minimal()
```


## Saving and Embedding Plots

You will, on occasion, need to save a plot to a specific file. Don't use the built-in "Export" button (this makes your work un-reproducible)! Instead, do this:

```{r}
weather_plot <- 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name), alpha = 0.5) + 
  theme_minimal()

ggsave("weather_plot.pdf", weather_plot, width = 8, height = 5)
```

Using these options when embedding figures should be fine most of the time. 

```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%",
  cache = TRUE 
)
```

You can fiddle around with these values depending on what you want your output file to look like. But sometimes this might not be worth your time.



















```















