---
title: "Simple document"
author: Waveley Qiu
date: 2021-09-16
output: github_document
---

```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

Let's write a new code chunk.

This code chunk imports the `tidyverse`, creates a data frame and makes a histogram.

```{r new_code_chunk, collapse=TRUE, message=FALSE}
set.seed(1234)

plot_df = 
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 + 2*x + rnorm(1000),
    y_quad = 1 + 2 * x^2 + rnorm(1000)
  )
plot_df

ggplot(plot_df, aes(x = x)) + geom_histogram()

ggplot(plot_df,aes(x = x, y = y)) + geom_point()

ggsave("output/scatterplot.pdf", height = 4, width = 6)
```

# Section 4

This is the learning assessment from the course website.

```{r learning_assessment, collapse=TRUE}
set.seed(20210916)
plot_df2 <-
  tibble(
    vec_rand = rnorm(500, mean = 1),
    vec_log = vec_rand > 0,
    vec_absnum = abs(vec_rand)
  )

ggplot(data = plot_df2, aes(x = vec_absnum)) + geom_histogram() + theme_minimal()

round(median(plot_df2$vec_absnum), 2)
```

The rounded median of the absolute values of the random sample from the normal distribution is `r round(median(plot_df2$vec_absnum), 2)`.


# YAML header options for html_document output
output:
    html_document:
      toc: TRUE
      toc_float: TRUE
      code_folding: hide
      
Specifying folder: rmarkdown::render(input="first_rmd.RMD", output_format="html_document", output_file="output/first_rmd.html")

```{r, echo=FALSE}
rmarkdown::render(input="first_rmd.RMD", output_format="html_document", output_file="output/first_rmd.html")
```


